Network Trait marker for working memory deficit in Schizophrenia: a multi site study

### 2016-02-25 manuscript.tex
改
逻辑不通；没有结合结果；语言太差

\documentclass[preprint,authoryear,review,12pt]{elsarticle}
%\documentclass[final,5p,times,twocolumn]{elsarticle}

@@

时间校正，头动校正，配准，降噪，滤波，空间平滑

@@

For every single site separately, the diagnose effect on each FC value was assessed using a two-sample t-test comparing images between SZ and NC from each site. A second level random effects meta analysis was used to pooling the single site statistics, in order to assess the replication of the effects from the entire dataset. The effect sizes were calculated using Hedge’s g, which provides an unbiased standardized mean difference that incorporates a correction for small sample sizes. Hedge’s g was calculated using each center’s t-statistic and the corresponding sample size. All significance thresholds were set to p < 0.001 FDR-corrected for multiple comparison. The meta-analysis was conducted in R with meta-for packages.

@@

Working memory is the result of various combinations of processes, no processes ((and correspondingly no brain structures)are unique or specific to working memory. ( Eriksson, 2015)Many brain regions interact during working memory and include "executive" regions in the PFC, parietal cortex, and basal ganglia, as well as regions specialized for processing the particular representations to be maintained, such as the fusiform face area for maintaining face information. Persistent neural activity in various brain regions accompanies working memory and is functionally necessary for maintenance and integration of information in working memory.

>>>>

\documentclass[preprint,authoryear,review,12pt,times]{elsarticle}
%\documentclass[final,5p,times,twocolumn]{elsarticle}

@@

%时间校正，头动校正，配准，降噪，滤波，空间平滑

@@

For every single site separately, the diagnose effect on each FC value was assessed using a two-sample t-test comparing images between SZ and NC from each site. A second level random effects meta analysis was used to pooling the single site statistics, in order to assess the replication of the effects from the entire dataset. The effect sizes were calculated using Hedge’s g, which provides an unbiased standardized mean difference that incorporates a correction for small sample sizes. Hedge’s g was calculated using each center’s t-statistic and the corresponding sample size. All significance thresholds were set to p \textless 0.001 FDR-corrected for multiple comparison. The meta-analysis was conducted in R with meta-for packages.

@@

Working memory is the result of various combinations of processes, no processes (and correspondingly no brain structures)are unique or specific to working memory( Eriksson, 2015). Many brain regions interact during working memory and include "executive" regions in the PFC, parietal cortex, and basal ganglia, as well as regions specialized for processing the particular representations to be maintained, such as the fusiform face area for maintaining face information. Persistent neural activity in various brain regions accompanies working memory and is functionally necessary for maintenance and integration of information in working memory.
